Analyses

### 2021-10-20 src/analysis/analyses.Rmd
add all source code

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Analyses](#analyses)
  - [Descriptive Results](#descriptive-results)
  - [Balance Checks](#balance-checks)
  - [Gender Hypothesis](#gender-hypothesis)
  - [Migration Hypothesis](#migration-hypothesis)
  - [Intersection Hypothesis](#intersection-hypothesis)
  - [Intersection Hypothesis -- Pooled](#intersection-hypothesis--pooled)

@@

# Analyses

@@

## Exploration

>>>>

# Scripts

@@

# Pre-Registered Analyses

@@

# Exploration

## Scaling fit

```{r "scale", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/explorative_cfa.R"))

```
